\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-01-16 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added source version of the workflow figure
adds a brief description of C-PML mesh layers created by CUBIT and the related configuration flags in Par_file

\begin{description}
\item [nummaterial\_velocity\_file] Defines the material properties. For fully defined materials, the formats is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where
\texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.

%%magnoni
For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
%For a tomographic model, the material definition format is:
%\begin{lyxcode}
%\texttt{domain\_ID} \texttt{material\_ID}  \texttt{tomography}  \texttt{name}
%\end{lyxcode}
%where
%\texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a negative, unique identifier, \texttt{tomography} keyword for tomographic material definition and \texttt{name} the name of the tomography file. The name is not used so far, rather change the filename defined in the file \texttt{model\_tomography.f90} located in the
%\texttt{src/generate\_databases/} directory.
%
\item [materials\_file] Contains the material associations for each element. The format is: 
\begin{lyxcode}
\texttt{element\_ID} \texttt{material\_ID}
\end{lyxcode}
where \texttt{element\_ID} is the element identifier and \texttt{material\_ID} is a unique identifier, positive (for materials) or negative (for tomographic models).
\item [nodes\_coords\_file] Contains the point locations in Cartesian coordinates of the mesh element corners.
\item [mesh\_file] Contains the mesh element connectivity.
\item [free\_surface\_file] Contains the free surface connectivity. You should put both the surface of acoustic regions and of elastic regions in that file;
that is, list all the element faces that constitute the surface of the model in that file.
\item [absorbing\_surface\_file\_xmax] Contains the surface connectivity of the absorbing boundary surface at the Xmax.
\item [absorbing\_surface\_file\_xmin] Contains the surface connectivity of the absorbing boundary surface at the Xmin.
\item [absorbing\_surface\_file\_ymax] Contains the surface connectivity of the absorbing boundary surface at the Ymax.
\item [absorbing\_surface\_file\_ymin] Contains the surface connectivity of the absorbing boundary surface at the Ymin.
\item [absorbing\_surface\_file\_bottom] Contains the surface connectivity of the absorbing boundary surface at the bottom.
\end{description}

@@

\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=.6\textwidth]{figures/workflow.jpg}
\par\end{centering}

@@

>>>>

\begin{description}
\item [absorbing\_cpml\_file] {\bf (only in case of C-PML absorbing conditions)} Contains at the first line respectively the "number of C-PML spectral elements"
and the "thickness of C-PML layers" (currently, a common thickness for all faces is defined but this can be easily adapted in the future if needed by the setting of CPML\_width\_x, CPML\_width\_y, CPML\_width\_z parameters). On all following lines are defined the "C-PML spectral elements global indexing" and "C-PML regions" for each
C-PML element according to the following convention:

\begin{itemize}
\item \#id\_cpml\_regions = 1 : X\_surface C-PML,
\item \#id\_cpml\_regions = 2 : Y\_surface C-PML,
\item \#id\_cpml\_regions = 3 : Z\_surface C-PML,
\item \#id\_cpml\_regions = 4 : XY\_edge C-PML,
\item \#id\_cpml\_regions = 5 : XZ\_edge C-PML,
\item \#id\_cpml\_regions = 6 : YZ\_edge C-PML,
\item \#id\_cpml\_regions = 7 : XYZ\_corner C-PML.
\end{itemize}

\item [materials\_file] Contains the material associations for each element. The format is: 
\begin{lyxcode}
\texttt{element\_ID} \texttt{material\_ID}
\end{lyxcode}
where \texttt{element\_ID} is the element identifier and \texttt{material\_ID} is a unique identifier, positive (for materials) or negative (for tomographic models or C-PML elements).
For C-PML absorbing conditions, \texttt{material\_ID} is a unique negative identifier between -2001 and -2007 in correspondance to the convention seen above in the description of the 
absorbing\_cpml\_file: -2001 <-> 1, -2002 <-> 2, etc\ldots

\item [nummaterial\_velocity\_file] Defines the material properties. 
\begin{itemize}
\item For fully defined materials, the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where \texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.

\item For C-PML absorbing conditions, , the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}
\end{lyxcode}
where \texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier between -2001 and -2007 to correspond with the definition given in materials\_file,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details. 
%
%For a tomographic model, the material definition format is:
%\begin{lyxcode}
%\texttt{domain\_ID} \texttt{material\_ID}  \texttt{tomography}  \texttt{name}
%\end{lyxcode}
%where
%\texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a negative, unique identifier, \texttt{tomography} keyword for tomographic material definition and \texttt{name} the name of the tomography file. The name is not used so far, rather change the filename defined in the file \texttt{model\_tomography.f90} located in the
%\texttt{src/generate\_databases/} directory.
%
\end{itemize}

\item [nodes\_coords\_file] Contains the point locations in Cartesian coordinates of the mesh element corners.
\item [mesh\_file] Contains the mesh element connectivity.
\item [free\_surface\_file] Contains the free surface connectivity. You should put both the surface of acoustic regions and of elastic regions in that file;
that is, list all the element faces that constitute the surface of the model in that file.
\item [absorbing\_surface\_file\_xmax] Contains the surface connectivity of the absorbing boundary surface at the Xmax \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_xmin] Contains the surface connectivity of the absorbing boundary surface at the Xmin \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_ymax] Contains the surface connectivity of the absorbing boundary surface at the Ymax \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_ymin] Contains the surface connectivity of the absorbing boundary surface at the Ymin \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_bottom] Contains the surface connectivity of the absorbing boundary surface at the bottom \\(irrelevant in case of C-PML absorbing conditions).
\end{description}

@@

\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=.6\textwidth]{figures/workflow.pdf}
\par\end{centering}

@@

\item [{\texttt{PML\_CONDITIONS}}] Set to \texttt{.true.} to turn on C-PML boundary conditions for a regional simulation. Both fluids and elastic solids are supported.
\item [{\texttt{PML\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.} to turn on C-PML boundary conditions on the top surface which by default constitutes a free surface of the model.
\item [{\texttt{PML\_WIDTH\_MIN}}] Gives a min. authorized bound to the solver to target an optimized thickness of C-PML layers. 
\item [{\texttt{PML\_WIDTH\_MAX}}] Gives a max. authorized bound to the solver to target an optimized thickness of C-PML layers. 
\item [{\texttt{f0\_FOR\_PML}}] Determines the dominant frequency that will be used in the calculation of: \\ ALPHA\_MAX\_PML = PI*f0\_FOR\_PML.
